    \input{theory/learning/entrepreneurship_education}

    \subsection{Digital Education}

    In recent times, e-learning has had a tremendous impact both outside and inside the classroom. With a growing teacher interest, research so far shows that digital education is hard, risky and possibly rewarding. \cite{luckin} Thus, digital education shows both great potential and great considerations.

    \subsubsection{Brining research into reality}

    Gates \cite{gates} has done a comprehensive study, which motivates why a digital tool or game is a good thing by showing a .33 standard deviations in intrapersonal learning outcomes, relative to non-game instructional conditions. They also conclude, that design rather than medium alone predicts learning outcomes.

    Much of the research to date on digital games has focused on proof-of-concept studies and media comparisons. The study's encouragement, is to focus on how theoretically-driven decisions influence learning outcomes: for the broad diversity of learners, within and beyond the classroom. Literature that have looked at mobile apps for learning specifically, are Godwin-Jones \cite{godwin-jones} and Page \cite{page}.

    %Godwin-Jones, R. (2011). Emerging technologies: Mobile apps for language learning. Language Learning & Technology, 15(2), 2-11.

    %Page, T. (2013). Use of Mobile Device Apps in Product Design. International Journal of Green Computing (IJGC), 4(1), 18-34.

    \subsubsection{Caring for the context}
    Luckin \cite{luckin} emphasises the need to care for the context. Stickdorn \cite{stickdorn} exemplifies how the design process should be altered when the context is social innovation.

    Service design in a social innovation context is called "social design", and is a new field. \cite{stickdorn}. No longer is service design solely focused on creating and promoting consumer goods, but to offer services to society. The design process should be designed to tackle a social issue, or with the intent to improve human lives. The focus is on delivering positive impact.

    \subsubsection{E-assessment}
    There are numerous examples of developments in e-assessment using mobile environments, as well as immersive environments and social and collaborative environments.

    Interest in formative e-assessment is increasing. A large amount of development has taken place on diagnostic testing environments, that allow teachers and learners to assess present performance against prior performance. \cite{luckin} For example, it has been shown that multiple-choice tests in e-assessment can be used to good effect \cite{nicol}.

    %Nicol, D. (2007). E‐assessment by design: using multiple‐choice tests to good effect. Journal of Further and higher Education, 31(1), 53-64.

    Luckin says that further consideration should  be given to how technology can be used to enable the assessment of knowledge and skills not usually distinguished within current curricula. \cite{luckin} One such example would be entrepreneurship.

    \input{theory/technology/technology}
