\subsection{Cognitive Psychology}
"How do you get people to learn things?" leads to asking "How do people forget? How do you make sure that people do not forget?". There are two principles: Bjork's Learning and Forgetting Lab at UCLA\citepp{learning-ucla} suggests that there are Retrieval practice vs. Spaces practice. Whereas Retrieval practice is about how retrieval of information from memory is more effective than those who read the same thing again and again to remember. The more effective students, retrieve from memory, e.g. they ask themselves "What was in that article?" instead of immediately reading the article. This kind of memory retrieval, is extremely effective for learning, research shows.

Spaces practice is about spreading out the learning with the purpose of not forgetting. Connected to this is e.g. the notion of meta-cognitive ability, and meta-memory, meaning how much personal insight you have into what you'll remember, and when you need to repeat information in order not to forget.

These describe research advances within cognitive psychology, and are connected to how our brain works in regards to our memory. Connected to the area of learning, is also "Desirable difficulties", "Scaffolding" and Cognitive load theory \citepp{effectivelearning-lab}.

A desirable difficulty, is when it feels like learning gets harder and harder, but in the long term you are actually learning more. Less people do it, as you do not get the same reward in return.

Scaffolding, is when step by step, you remove the support wheels for the user. E.g. you may start with easy questions using multiple choice, but eventually graduates into using flashcards as principle \#1, if the user can master it.

Cognitive load theory asks "How do you design for the mind?", and "How much information can we store in our work memory?". For example, research shows that visual input and audio input (voice and audio) are stored in separate memory channels, meaning that use both mediums are often a good choice. There are three types of cognitive load, "intrinsic", "extrinsic" and "germane".

\input{theory/learning/pedagogical-development/taxonomy}

\subsection{Social Psychology}

"How do you get people to behave differently?" looks at motivation theory. Kathy Sierra, author of Badass: Making Users Awesome\citepp{interactiondesign-badass}, researches how \textit{learning is tied to product development}. She says that our product development should be led by a focus on building great users, instead of great products. She takes a stance in "How do you build expertise?".

While emphasizing e.g. cognitive load theory, Sierra looks a lot at motivation. How to get people to continue to build expertise or using an app, self-determination theory is a good area of research. The book Drive: The Surprising Truth About What Motivates Us\ref{motivation-drive} is a good basis, which pushes that if Autonomy, Mastery and Purpose is present, this fosters drive.

Another insight Sierra shares is that we should start taking about Post-UX-UX: what happens after your product has been used? How do you design \textit{that} experience? Here, service design is a step towards actively working with how your app fits in a larger context \citepp{servicedesign-ideo}.

In physical as well as digital training, smart individual feedback is of high importance. Feedback should be task-oriented, always \textit{informational}. An example might be: "I see that you're ranking number \#1 in the subject of X, may I suggest Y?". The carrot-stick method (e.g. giving achievement points or rewards) is sub-par with motivating learning in itself for the user. Therefore, feedback should not be in a motivational form, e.g. saying "You're good!". Triggering the enthusiasm for learning, is a more effective strategy.

\input{theory/learning/pedagogical-development/building_expertise}

\subsection{Training Transfer}

Finally, \textbf{"How do you make sure a course gives effect in your everyday life?"} looks at Training transfer. For a long time, the focus on learning effectiveness in leadership trainings has been to maximize the quality of the lectures themselves. Recently, the focus has shifted into researching how the before and after of the training affects the learning. If the leader is involved with the participants before the training, and communicates expectations, and gives the participants support afterwards, it leads to increased success. On the other hand, the leader can kill the learning of a whole education program, by simply saying the wrong words before an education is held. As a lot of trainings are now based on research, and quality of trainings thus has increased dramatically, this is where a lot of learning potential is. This is connected to both concepts included in "How do you get people to learn things?" and "How do you get people to behave differently?". \\

\subsubsection{The Importance of Before and After}

\textbf{Robert O. Brinkerhoff - Making L\&D Matter : Learning Technologies 2013}
% https://www.youtube.com/watch?v=__wUZzJV8lM

De visar att före/efter är lika viktigt som själva träningen

%http://blog.dronahq.com/dr-robert-o-brinkerhoff-making-learning-development-ld-matter/

\input{theory/learning/pedagogical-development/reflection_assessing}

% Growth mindset or Mastery orientation
% http://www.strivetogether.org/growth-mindset-or-mastery-orientation
