\section{Application Implementation}

In this section, the prerequisites for the app is described, from the perspective of the user, stakeholders, and the developer.

\subsection{User Needs}

The technical constraints for the project, would need to affect the technologies used, if the project would be user-centered. On the client side, the app would need to be mobile and web based, consider non-access to internet, and not use a lot of battery, to work for the coaches of YoungDrive. That the app should be simple to use in this cultural setting leaded to design constraints and needs for evaluation.

\subsection{Stakeholder Meeds}

As the project was only three months, and the first month would be without digital development, time constraints were massive. However, to be able to answer how design affects learning, evaluation was needed to be done via data collection.

If no evaluation, there would be no need to write code, instead working with a low-fidelity prototype using pure design tools. Now, a data-driven approach was needed to measure, and therefore an app needed to be developed. On the server side, a database and API would be needed, to pull data from the database and push data from the client. Since internet was not always available, the client must be smart in its usage of pushing and pulling data. This would need to be investigated further into the project.

\input{methods/application-implementation/iteration_1}

\input{methods/application-implementation/iteration_2}

\input{methods/application-implementation/iteration_3}

\input{methods/application-implementation/iteration_4}

