\chapter{Methods and Implementation}\label{cha:Method}

% längsta avsnittet i rapporten. Den består av en redogörelse av ditt arbete och den visar hur du kommer fram till dina resultat.

% Undvik egna synpunkter. Dessa framförs i Inledningskapitlet och Diskussions-kapitlet

% Ange källa till figurer i slutet. T.ex.  Source: Expedition Mondial.

% Metoddelen beskriver tillvägagångssättet – intervjuer, observationer, litteraturstudier, laborationer och så vidare. Motivera varför en viss metod valdes och vilka eventuella svårigheter som har förekommit. Metoden ska vara replikerbar, vilket innebär att en annan skribent ska kunna göra om studien med hjälp av informationen i metoddelen. Det finns en mängd böcker om olika vetenskapliga metoder. Till exempel kan en intervju utföras på en mängd olika sätt. I rapporter inom humaniora brukar metoddelen vara mer utförlig än i en teknisk rapport.

This chapter presents the methodological framework, via presenting methods to design for learning and motivation.

Then, the setting and research context is described, together with a description of the participants.

Then, application implementation is described, followed by presenting the study design and data collection.

The final topic is data analysis theory.

\section{Methodological framework}

\input{methods/methodological-framework/methods_learning}

\input{methods/methodological-framework/methods_motivation}

\input{methods/methodological-framework/methods_awesome_users}

\input{methods/methodological-framework/methods_design_process}

\input{methods/methodological-framework/methods_service_design}

\input{methods/methodological-framework/methods_digital_service_design}

\input{methods/methodological-framework/methods_data_collection}

\section{Setting and research context}
Uganda (Kampala, Tororo) and Zambia (Kabwe).

The biggest challenge with regards to time constraints and cultural differences is that it is difficult to understand the audience.

It led to me choosing to spend 3 months in Uganda, because the client and academy is there, and start the design process when I'm there. It also led me to wanting to apply service design.

By being in Uganda and applying service design, I will come closer to the client and coaches.

The internet is worse, especially outside Kampala (I will not be able to access 4G, and prices are high).

Working mainly from Kampala, because that is where YoungDrive is situated, means that there is still a long distance to the coaches in Tororo, which is located near the Kenyan border.

\section{Subjects (Participants) \& Stakeholders}

Lorum ipsum.

Participant manual and Coach guide

\input{methods/study_design}

% Application implementation
\input{methods/application_implementation}

\input{methods/data_analysis_theory}
