\section{Study Design and Data Collection}

  As a computer expert with social skills needing to design and develop an app for an unfamiliar cultural and socio-economic context, it was needed to quickly become a good designer. The technical aspect of the project was but one. It was needed to learn how to develop hybrid apps in JavaScript that worked offline, and had an online back-end. However, those are merely the technical demands.

  It was needed to quickly become a good designer, not mainly from a perspective of graphic design or interaction design, but \textit{how} to explore, design, and implement what the user needs from the requirements "fun, user-friendly, and good for learning". There was also a need to evaluate the effectiveness of the implementations, to assess learning and the interaction design aspects of desirability, utility, usability and pleasurability. The approach used to learn design from these perspectives was to read extensive literature, consult a diverse set of experts, and be humble and curious in interactions with the end-users and stakeholders. In the following section, the creation and implementation for a suitable design process is described, together with the study design and data collection for each iteration of the project.

\input{methods/study-design/implementation_design_process}

%\input{methods/study-design/implementation_methods}

\input{methods/study-design/iteration_1}

\input{methods/study-design/iteration_2}

\input{methods/study-design/iteration_3}

\input{methods/study-design/iteration_4}
