\chapter{Conclusions and Future Work}\label{cha:conclusion}
% important to relate to the Purpose

% Sätt av ett kort kapitel sist i rapporten till att avrunda och föreslå rikningar för framtida utveckling av arbetet.

In response to the research questions questions, the master thesis has: %investigate if the work can:

\subsubsection{Contributed to the domain of entrepreneurship education in a developing country context}
This research shows that an app can be effectively used during and after training to assess and learn entrepreneurship. Furthermore, the app can also prepare coaches before youth sessions, training them both in entrepreneurship and preparing their lessons.

In \textit{addition}, this has been done in a developing country context, with coaches having no prior smartphone experience. The app is used for coaches in conjunction with a physical entrepreneurship training today, and does not yet address the youth themselves, or replaces the physical training.

However, the research shows that both the teacher and the coaches greatly appreciates the support the app has given them. As entrepreneurship to its nature is practical in many aspects, one finding is how multiple-choice questions can still simulate real learning, by design solutions such as asking "Are you sure?", giving personal feedback, and formulating questions as scenarios.

\subsubsection{Demonstrated how certain technical constraints and design constraints can be overcome in a developing world context} % service design in development environments % Designprocessen, frågeställning 1
As devices were limited, a goal was to make the app available on as many devices as possible. Creating a hybrid app using web technologies using Meteor made the app available both as a native app on Android and iOS devices, as well as on the web.

As internet is accessible but expensive and often used seldom, the app does not provide rich media or simulations, but focuses instead on creative design possibilities using multiple-choice.

Most of the coaches being first-time smartphone users, letting them continuously test and co-create the app has created a tailor-made app from their needs and conditions. It may be surprising how simple design solutions using text and clear visuals can provide rich learning feedback.

That the app should work offline, and still be able to push quiz results when it gets online, has been a challenge. It can be hard to find good existing approaches for some technical platforms, but for Meteor plugins such as GroundDB proved very usable.

An insight is how quickly the coaches have increased their fluency with using the smartphone and the app. Even though the design at first needs to be very simple, as long as features are introduced slowly and as intuitive, the app could become more complex over time, to the point where no compromises needs to be made.

When it comes to overcoming cultural differences, learning from the expertise of local partners and tech companies can not be overestimated. They have been very willing to share previous mistakes, learnings and successes. This has saved a lot of time, and made the sparse amount of interactions and development time so much more efficient. Also, the value of getting to know the coaches on a first-hand basis has been greatly beneficial. The app has been designed together with them as co-creators, with a developed mutual interest and understanding, having a common goal of creating an app that works for their needs.

\subsubsection{Provided methods of investigating usability and learnings with a digital training tool in the real-world training context} % Utvärdering, frågeställning 2

To investigate usability, observations using think-aloud in the real-world training context proved the most effective. In big groups, data could give tendencies on common problems that needed to be adressed. In smaller groups, ideas and precise feedback was more common. It helped having a framework to compare usability against, in this case the interaction design principles of desirability, utility, usability and pleasurability.

To investigate learning in the real-world training context, literature research and data analysis of quiz results was highly beneficial, but mostly when put into the context of the observations made in the real-world training context.

Surprisingly often, comparing research and expert opinions with what coaches thought was best for learning, was in unison. When this happens, the self-confidence of the designer can increase, and the designer can be more daring and experimental.

Having much testing and co-creation was a very rewarding approach. To make it truly testable, lo-fi and hi-fi prototypes should be used instead of hypothetical questions. While research before starting to develop is a great start, it was trying different solutions, all based on user advice, expert opinion and research, that gave great results.

\subsubsection{Created new methods in service design, when co-designing digital artefacts in a developing country context}
Short iterations is a challenge, especially when time is sparse and the culture is different than one's own. Often in projects, testing is overlooked. In this project instead, service design helped to look at the users as not only testers, but as co-creators. This is not new in itself, but the creation of Digital Service Design, and methods within this discipline, were new. Examples include sevice mini-sprints and field hackathons.

Interactions with the coaches always included Service Mini-Sprints (see \ref{mini-sprint}), allowing the most important feedback and insights to be addressed in the app and workshop formats already the next day. This allowed for very effective use of the sparse interactions with the coaches, and there was no need to wait for the next iteration to test the coaches' feedback.

The "field hackathon", in which the app was refined and tested each day of the coach training, was the most important piece of the whole master thesis. More than the opportunity to develop the app with the coaches, it had the extra benefit of giving the opportunity to observe the YoungDrive training and understand the coaches.

To use a service design approach when co-creating digital artefacts in a developing country context proved highly effective, and it is recommended that this are is further studied. It does demand bravery of the designer to get to know the users so well, and design for their needs and dare to question the client, but in the end, as in this case, both the users and the client may end up more satisfied with the result.

\input{discussion/future_work}
