\subsection{The Client: YoungDrive}

In this section, the project that the client YoungDrive is in is first described, and then how YoungDrive  fit into the structure with its entrepreneurship education program. In the last part, future plans of YoungDrive and A working future is presented, giving relevancy to the field of digital education.

\subsubsection{A working future}

Plan International works towards eliminating child poverty, and their project A working future, supported by SIDA 2012-2016, tackles unemployment among youth in rural areas.

It runs for 12 000 youth in Kamuli and Tororo.

\subsubsection{VSLA groups and CBT's}

Because of high tuition fees, saving (financial literacy) and earning (practicing vocational skills) are central.

VSLA groups have existed for many years, where a group starts a village savings and loans group together. A democratic process makes the group independent of e.g. banks, which rates are in general high and which may not even borrow money, either because of long distances to the bank or of no previous financial history.

For Plan International, VSLA groups have been successful in several countries for a long time. However, while the groups were skilled with saving, they did not always spend the money in the most strategic way.

Plan's pilot with A working future, was to introduce trainings on top of the VSLA structure.

Where Community Based Trainers (CBTs) were previously only responsible for hosting the groups, not they were trained and tasked with carrying out different programs: like agriculture, financial literacy, and the most successful program to date, focusing on running own businessess, YoungDrive.

\subsubsection{YoungDrive}

YoungDrive is based on a Swedish concept, and had previously had a pilot in Botswana, when tasked with running the entrepreneurship module of A working future. The organization foster and educate young entrepreneurs in developing countries. They train the CBT's, provide training material, and support the CBT's via direction and direct support via co-project leaders and Youth Mentors (YMs).

YoungDrive moves an entrepreneur to location, becoming country manager. Then, she educates project leaders during four days, followed by educating CBT's, which then roll out the training to the youth groups during 10 sessions, 1 session per week in average. The CBT's also rolls out other trainings, often simultaneously.

\subsubsection{Social entrepreneurship}

The CBT's are often volunteers, receiving a small scholarship from Plan International. They are often business owners themselves.

Thus, the CBT's can be described as social entrepreneurs. As Mitchel says about entrepreneurship \cite{mitchel}, motivation does not need to be wealth accumulation anymore. The activity of entrepreneurship contributes to society, in a way that is not caputed by the commercial entrepreneurship literature.

Many of the YoungDrive participants are driven by that their business can have an impact on their community, as well as take them out of unemployment or increase their current livelihood.

\subsubsection{Future plans}

For the future of YoungDrive, they want to make the CBT's even better, and collect and take us of data (monitoring and evaluation). Another motivation is scaling and monetization, as Plan International wants to increase the project to more countries, with an increased digital focus, and YoungDrive wants to be independent of project funding (i.e. a social enterprise). This was a great time to introduce digital enablers, where there previously had been no technology-focus, especially towards CBT's and YM's.
