\subsection{Entrepreneurship Education, YoungDrive}

% Det viktigaste är att sätta in läsaren i ämnet och visa hur du tänkt behandla ämnet i resten av rapporten. Det gör du under rubriken Bakgrund.

En halv miljard unga människor i lever i arbetslöshet runt om på jorden (enligt World Economic Forum) och ungdomsarbetslösheten i utvecklingsländer brukar kallas för en tickande bomb.

The team behind YoungDrive works to foster and educate young entrepreneurs in developing countries. In 2015, 12 000 entrepreneurs in Uganda were educated in starting their own businesses and the ambition is now to to scale the program to more locations.

The entrepreneurship education concept is to work as a plugin to organizations with existing structures on place. Today, the education is held for Plan International in two areas in Uganda, Kamuli and Tororo. This is how it works:

% Nämna ett exempel på struktur kan vara en mikrolån-grupp

\begin{itemize}
    \item YoungDrive moves an entrepreneur to the location, which becomes Country Manager %Young Drive flyger ner en entreprenör som blir Country manager.
    \item Who educates 6 local project leaders (4 days) %Som utbildar 6 lokala projektledare (4 dagar).
    \item Which educates 25 coaches in the 2 locations (5 days) %Som i sin tur utbildar 60 coacher (5 dagar).
    \item Which finally roll out the training to the youth groups (10 sessions) %Som slutligen rullar ut Training of ungdomsgrupperar (10 tillfällen ).
\end{itemize}

The entrepreneurship education program YoungDrive now requests two digital modules, to reach even better results and to be able to scale up the operations to more locations with confidence. The overall aim of my Master thesis is to do a Minimum Viable Product (MVP) of module 1, the Coach module. The master thesis is about how to design an app for entrepreneurship education, including evaluating it's effectiveness towards the coaches. The result is an app which the coaches use during and after the coach training.