\section{Background}

    %\input{introduction/background/a_working_future}

    %\subsection{Digital Education}

    In this section, the background of the master thesis is presented.

    The first section describes the opportunities for entrepreneurship in Uganda, followed by how Plan International and YoungDrive uses this to tackle child poverty by fostering and educating youth in starting their own businesssess. This section concludes by how digital learning and digital tools becomes increasingly demanded, which is why this master thesis has emerged.

    The final section so gives a background to the status of digital education today, followed by related work to the thesis.

    All of this together leads up to the purpose of the master thesis.

    \input{introduction/background/entrepreneurship_uganda}

    \input{introduction/background/plan_youngdrive}

    \subsection{Digital Education}

    In recent time, e-learning has had a tremendous impact both outside and inside the classroom. With a growing teacher interest, research so far shows that digital education is hard, risky and possibly rewarding. Thus, digital education shows both great potential and great considerations.

    \subsubsection{Brining research into reality}

    Gates \cite{gates} has done a comprehensive study, which motivates why a digital tool or game is a good thing by showing a .33 standard deviations in intrapersonal learning outcomes, relative to non-game instructional conditions. They also conclude, that design rather than medium alone predicts learning outcomes.

    Much of the research to date on digital games has focused on proof-of-concept studies and media comparisons. The study's comparison, is to focus on how theoretically-driven decisions influence learning outcomes: for the broad diversity of learners, within and beyond the classroom.

    \subsubsection{Caring for the context}
    Luckin \cite{luckin} emphasises the need to care for the context. Stickdorn \cite{stickdorn} exemplifies how the design process should be altered when the context is social innovation.

    Service design in a social innovation context is called "social design", and is a new field. \cite{stickdorn}. No longer is service design solely focused on creating and promoting consumer goods, but to offer services to society. The design process should be designed to tackle a social issue, or with the intent to improve human lives. The focus is on delivering positive impact.

    \subsubsection{E-assessment}
    There are numerous examples of developments in e-assessment using mobile environments, as well as immersive environments and social and collaborative environments.

    Interest in formative e-assessment is increasing. A large amount of development has taken place on diagnostic testing environments, that allow teachers and learners to assess present performance against prior performance. \cite{luckin}

    Luckin says that further consideration should  be given to how technology can be used to enable the assessment of knowledge and skills not usually distinguished within current curricula. \cite{luckin} One such example would be entrepreneurship.

    \input{introduction/background/related_work}
