\chapter{Introduction}\label{cha:intro}

%Ge läsaren en introduktion till rapporten genom att sätta in läsaren i ämnet. Presentera ej resultat eller detaljerad information.

%Inledningsvis, gör:
%Redogör för syftet och frågeställningar
%Redogör den använda metoden
%Bakgrundsbeskrivning
%- sätt in läsaren i ämnet
%- tidigare forskningen på området
%Redogörelse av resultat, referera och relatera till tidigare forskningen
%Knyt ihop resultaten, analysera dessa, och sätt in resultaten i ett vidare perspektiv

This chapter is the introduction to the master thesis report. An app for entrepreneurship coaches could, if successful, help coaches to assess and learn to become better with teaching entrepreneurship to youth.

There are both opportunities and challenges for mobile tools for rural areas of Uganda. While entrepreneurship activity is high, and mobile services are growing rapidly, the two fields have not yet been combined for entrepreneurial learning in a developing country context.

The non-profit YoungDrive teaches entrepreneurship to youth in developing countries, with coaches now educating youth in Plan International's project in Uganda, and an ongoing training pilot in Zambia. YoungDrive wants to see if an app can make the coaches even better, and if the data from the app can support monitoring and evaluation.

To answer this need, entrepreneurship education and digital education has been researched together with how to develop apps for web and mobile platforms simultaneously.

The introduction is concluded with related work within digital tools in developing countries, and doing digital assessment and mobile learning, before presenting the research questions.

The research questions takes into consideration both development, design, learning, usability and process, from a developing country context of developing a tool for entrepreneurship learning.

\input{introduction/purpose}

% \input{introduction/3_limitations}

%\input{introduction/definitions}

\input{introduction/background}

\input{introduction/research_questions}

%\input{introduction/4_method}

%\input{introduction/5_discussion}

%\input{introduction/6_structure}

%\subsection{Typography conventions}
