\section{Purpose}
\label{purpose}
%Under rubriken Syfte redogör du för själva frågeställningen och syftet med rapporten. Förklara vad rapporten ska handla om och vad du hoppas kunna uppnå för resultat. Definiera begrepp som inte är kända för målgruppen.

In order for young ambitious entrepreneurs to build sustainable enterprises they need to have basic entrepreneurial skills. This is where a mobile learning platform comes into the picture.

\subsection{An app for the entrepreneurship coaches}
The entrepreneurship education YoungDrive is an initiative of Illiana Björling from YoungDrive, now collaboration with Plan International. Within the project A working future, they have educated, supported and inspired 12 000 Ugandan youth in the process of starting their own businesses. \citep{nissar}

YoungDrive now requests two digital modules, to reach even better results and to be able to scale up the operations to more locations with confidence.

The overall aim of the master thesis is to do a Minimum Viable Product (MVP) of a entrepreneurship coach training app. The master thesis is about how to design an app for entrepreneurship education, including evaluating it's effectiveness towards the coaches.

The result is an app which the coaches use during and after the coach training.

\subsection{Definition of success for the app}

By training coaches that can carry out the education in larger groups of entrepreneurs, the education reach many young people at the same time. A mobile learning platform is predicted to improve the effect of the training even more, by fulfilling the following purposes:

\begin{itemize}
  \item Validate the coaches' level of knowledge during their education
    \item Train the coaches on distance
    \item Certify all staff
\end{itemize}

YoungDrive's experience goal for the app is "It should be easy to understand, pedagogical and enjoyable to use, and the coaches should think it is fun and meaningful to learn via the app". \citep{youngdrive-masterthesis-idea}
