\subsection{Entrepreneurship in Uganda} % https://www.linkedin.com/pulse/social-innovation-entrepreneurship-uganda-why-mobile-services-nissar?trk=prof-post

    %This section will present background on working with mobile learning platforms, and understanding the society of entrepreneurs in Uganda.

    %\subsubsection{Why Uganda is Ranked the World's Most Entrepreneurial Country}
    A couple of prominent facts helps to portrait entrepreneurship activity in Uganda:

    \begin{itemize}
      \item Uganda can be ranked the world's most entrepreneurial country (with 28\% of the population considered entrepreneurs \citep{goodis})
        \item Uganda is ranked the youngest population in the world (78\% of all Ugandans are below 30 \citep{unPopulation})
        \item Uganda has a very high unemployment rate (62 \% of people between 18–30 are unemployed \citep{lostopportunity})
    \end{itemize}

    % Ytterligare beskrivning av land: http://www.sun-connect-news.org/countries/uganda/

    With a high unemployment rate and little or none social security, starting a business is for many young entrepreneurs simply a tool for survival. But tough conditions can also lead to creativity, and there are as well many innovative entrepreneurs with great ideas and the aim to create positive social impact \citep{nissar}. As \cite{mitchel} says about entrepreneurship, the motivation of entrepreneurship does not need to be solely wealth accumulation anymore. The activity of entrepreneurship contributes to society, in a way that is not captured by the commercial entrepreneurship literature. No matter the reason of starting a business, Uganda's many entrepreneurs are contributing to the national society by boosting the economy and creating new jobs.

    \input{introduction/background/theory/entrepreneurship_education}

    \subsection{YoungDrive}

    \cite{youngdrive-web} is based on a Swedish concept, and had previously had a pilot in Botswana, when tasked with running the entrepreneurship module of A working future for Plan International. The organization fosters and educates young entrepreneurs in developing countries. They train the coaches, provide training material, and support the coaches via direction and direct support through co-project leaders and Youth Mentors.

    YoungDrive moves an entrepreneur to location, becoming country manager and "teacher". The teacher educates project leaders during four days, followed by educating coaches, which then roll out the training to the youth groups during 10 sessions, 1 session per week in average. The Community Based Trainers (CBTs) also rolls out other trainings, often simultaneously.

    For the future of YoungDrive, they want to make the CBT's even better, and collect and take use of data (monitoring and evaluation). Another motivation is scaling and monetization, as Plan International wants to increase the project to more countries, with an increased digital focus, and YoungDrive wants to be independent of project funding (i.e. a social enterprise).

    Given the above, this was a great time to introduce digital enablers for YoungDrive, where there previously had been no technology-focus, especially towards CBT's and Youth Mentors. The master thesis is the first project which focuses on digital enablers for YoungDrive.
