\subsection{Service design methodology}

Below, brief descriptions of the five principles of service design is described, together with how the work is divided into iterations, and examples of tools that can be applied.

\subsubsection{The five principles}
Stickdorn \cite{stickdorn} describes five principles that constitute service design thinking, and how to follow these.

The book describes how to follow these principles, by making the process user-centered (e.g. via design ethnography), co-creative (involve all stakeholders) and holistic (keep the big picture). Sequencing (visualize the service, and make iterations) evidencing (make the service tangible) are the two last important principles.

\subsubsection{Sequencing: The iterative process}
While literature and practice refer to various frameworks, with different number of steps, every service design project includes: exploration, creation, reflection and implementation \cite{stickdorn}.

Nissar \cite{expedition-mondial} suggests a model where one iteration consists of insights, ideation, trigger material, and interactions.

The iterations should come closer and closer to a desired outcome. It is not always obvious what this outcome is. For each iteration, the process takes the project closer, from Why? to What? to How?, often with overlaps \cite{expedition-mondial}.

\subsubsection{Tools}

There are a number of popular service design tools that follows the five principles, e.g. how to make it user-centered.

Explorative tools are e.g. Shadowing, Customer Journey Map, Contextual Interviews, The 5 Why's (same as "Why-why-why" within interaction design \cite{thoughtful}), Cultural Probes, Mobile Ethnography and Personas.

Tools to create and reflect can be done via a certain work methodology, e.g. agile development, and structuring and inspiring brainstorms, e.g. via "What if...?" and Co-Creation, inviting stakeholders in the creation process.

%\input{theory/design/service-design/social_innovation}

%\subsubsection{Service Design Thinking}

%\input{theory/design/service-design/methodology}

%\input{theory/design/service_design_stoff}
