\chapter{Methods and Implementation}\label{cha:Method}

% längsta avsnittet i rapporten. Den består av en redogörelse av ditt arbete och den visar hur du kommer fram till dina resultat.

% Undvik egna synpunkter. Dessa framförs i Inledningskapitlet och Diskussions-kapitlet

% Ange källa till figurer i slutet. T.ex.  Source: Expedition Mondial.

% Metoddelen beskriver tillvägagångssättet – intervjuer, observationer, litteraturstudier, laborationer och så vidare. Motivera varför en viss metod valdes och vilka eventuella svårigheter som har förekommit. Metoden ska vara replikerbar, vilket innebär att en annan skribent ska kunna göra om studien med hjälp av informationen i metoddelen. Det finns en mängd böcker om olika vetenskapliga metoder. Till exempel kan en intervju utföras på en mängd olika sätt. I rapporter inom humaniora brukar metoddelen vara mer utförlig än i en teknisk rapport.

This chapter presents the methodological framework, via presenting methods to design for learning and motivation.

Then, the setting and research context is described, together with a description of the participants.

Then, application implementation is described, followed by presenting the study design and data collection.

The final topic is data analysis theory.

\section{Methodological framework}

\input{method/methodological-framework/methods_learning}

\input{method/methodological-framework/methods_motivation}

\section{Setting and research context}
Uganda (Kampala, Tororo) and Zambia (Kabwe).

\section{Subjects (Participants) \& Stakeholders}

Lorum ipsum.

\section{Study Design \& Data Collection}

\input{method/study-design/method_design_process}

\input{method/study-design/method_service_design}

\input{method/data_collection}

\subsection{Preparations in Sweden}

The insights before going to Uganda were addressed in the initial work plan, see Appendix A. \todo{Add appendix with Work plan}

\input{method/methodological-framework/iteration_1}

\input{method/methodological-framework/iteration_2}

\input{method/methodological-framework/iteration_3}

\input{method/methodological-framework/iteration_4}

% Application implementation
\input{method/application_implementation}

\section{Data Analysis Theory}

\subsection{General}
%Methods to choose from for analysing (i.e. what I did during the interactions, to test and analyze my app)

%Partly data collection done via app, but also all the observations

\subsubsection{How to measure effectiveness}

Answering research question \#2 was a matter of choosing how to measure effectiveness. After choosing what should be evaluated, there needs to be a careful balance between what should be understood via interviews with the target group, and data collection via the app. There are three main aspects that are interesting:

These ways of measuring the questions are subject to change.

%Effectiveness measurements.

\begin{itemize}
    \item
    \textbf{How do users interact with the app?} (Usability) Do they want to use it more on a voluntary basis?
    \textit{(Measure)} and determine why \textit{(Interview and Measurement)}. "Did you feel you needed any support? Did the app help? Did you need to search for support elsewhere?"

    \item \textbf{What usability aspects are associated with using the app?} (Usability) Do they like it? Ask: Are they stimulated? If not, why? What didn't they like? \textit{(Interview)} When can they use the app, and when are they not able to?

    \item \textbf{What learning outcomes are associated with using the app for the coaches?}  (Learning of Entrepreneurial Knowledge))
    How good are they at answering the questions? 1.
    \textit{(Measure)} What percentage of the answers were correct/inorrect?  2. \textit{(Interview)} Were the answers were correct/incorrect because of lack of knowledge or wrong formulated?

    Ask the teacher/country manager/project leader if they got valuable information. Ask: did it help them become a better teacher? Were the results trustworthy? \textit{(Interview)}

    \todo{Insert Josefina's quote here}

    Do they want to improve their knowledge via the app? This can be measured via how many times they repeat a test, what material they are studying for (e.g. measuring active time spent reading each section).
\end{itemize}

\subsection{Iteration \#1}
%Here I used:

\subsection{Iteration \#2}
%Here I used:

\subsection{Iteration \#3}
%Here I used:

\subsection{Iteration \#4}
%Here I used:

\subsubsection{Quantative data collection}

This was the first time that the server could collect data. See previous section for how the data collection was done and processed.

\subsubsection{Qualitative data collection}
Every coach was divided into one or three groups, on random. In these groups, they were asked:

\begin{enumerate}
\item Why do you think you were correct or incorrect?
\item Do they like the app?
\item Are you stimulated by the app?
\item What did you like?
\item What did you not like?
\item When do you want to use the app?
\item When are you not able to use the app?
\end{enumerate}
