\section{Answering research questions \#1}

\textbf{\textit{How the topic of Entrepreneurship affects the work}}\\
The scope of the app is to examine the entrepreneurship the student already has. The goal is to give good feedback.

Entrepreneurship is a developing area of research. The topic and the YoungDrive's methology largely effects the work, via its ethos "Dream big, start small", "Can you sell?", and emphasis on fun. Their existing training material and the structure of the program needs to be taken in consideration.

Entrepreneurship means using a learning by doing methodology. A challenging part of the work is that YoungDrive consists of both the practical skills of the entrepreneur, theoretical material of running a business, and an entrepreneurial mindset. Therefore, both how to assess knowledge, and build habits, needs to be examined.

\textbf{\textit{How a Physical education affects the work}}\\
The physical vs. digital interplay needs to be closely examined. How does the app interplay with the physical education? For this, service design methodology will be used. \\

\textbf{\textit{How the Time Constraints and Cultural Differences affects the work}}\\

The biggest challenge with regards to time constraints and cultural differences is that it is difficult to understand the audience.\\

Action:
\begin{itemize}
    \item It led to me started planning the master thesis several months ago
    \item It led to me choosing to spend 3 months in Uganda, because the client and academy is there, and start the design process when I'm there
    \item It led me to the topic of Service Design
\end{itemize}

Positives:
\begin{itemize}
    \item I will come closer to the client and coaches by moving to Uganda, which is necessary when taking a service design approach
\end{itemize}

Negatives:
\begin{itemize}
    \item I will have limited internet outside of the work location
    \item Long distances between work place and home compared to Sweden
    \item I will still have long distances and limited access to coaches\\
\end{itemize}

These negatives needs to be overcome, by narrowing down the scope of the thesis work. \\

\textbf{\textit{How the Design Constraints affects the design process}}\\
"Simple" in this cultural setting leads to design constraints and that design methodology becomes very important.\\

\textbf{\textit{How the Technical Constraints affects the technologies used}}\\
Limitations on internet/electricity means:

\begin{itemize}
    \item Web app
    \item Localized
    \item Database
    \item Fetch/pull functionality in the app
    \item Battery preserving app needed
\end{itemize}

Also, me as a developer have limited experience of building apps, and time constraints. As such, technical compromises should be made.

Furthermore, existing tools could be used, instead of building the app from scratch. E.g. using existing tools like Knowly or Typeform\footnote{examples include https://showroom.typeform.com/to/ggBJPd and https://showroom.typeform.com/report/njdbt5/dIzi} during the first iterations for understanding users, and during development e.g. the Typeform API (http://typeform.io/). The Typeform API allows developers to create surveys from within their own applications or systems. \\
