\subsubsection{Data observations}

% Important to be objective
% En diskussion om hur resultaten kan användas i praktiken är också i de flesta fall belysande och relevant i rapporter

% https://liu.se/ias/kontakta-oss?l=en

In this section, the conclusions from the different group characteristics are presented.

Early observations from the pre-test data was that a surprising number of cells were left blank. One user had not done the pre-test, where some had left questions unanswered (most commonly "Do you own a company?" (should have used the word "business"), plus "Hours of preperation" and "Occations for a youth session" (there is a tendency this might be because they were not proud of their answers, because of correlations with low quiz results).

Missing cells was not as obvious with the app results, were users could not progress in a quiz without answering both the question and the confidence. However, none of the passed quiz 9 certification answers had been submitted. Thus, it was needed to add these from the manual recordings, which had been used as a backup in case anything like this would happen.


There were a number of quick insights that could be drawn before the parallell coordinates visualization: there was a surprisingly low number of answers where the user answered the question without confidence. Also, more users had started a quiz without finishing it than anticipated. Finally, a lot of users had done quizes that were not Topic quiz 3 and Coach quiz 9, which might indicate high interest (if they did more than 2 quizes) or confusion (if they did not do 3 or 9, but they did do other quizes) during the app evaluation. This meant that on some aspects, there were less data than anticipated, (which was troublesome, as there were already few data points), and some aspects where there was more data than anticipated (that were overlooked).

First-hand insights before the parallell coordinates were that there was a strong corrolation between pre-quiz results and quiz 9 try 1 (slightly visible also in quiz 3 try 1, but with more outliers). Also, with manuals there was a higher probability to finishing quiz 9 training + certification.

\subsubsection{Statistical analysis}
Statistical analysis unfortunately showed that none of the results were statistically significant to be notable using linear regression, or any of the other statistical methods detailed in the methodical framework.

\subsubsection{Parallel coordinates visualization}
The interactive parallel coordinates visualization could give many more insights, more faster than the static presentations in Google Sheets.

\textbf{Youth mentor (brun), 6 st vs. CBT (blå), 14 st}
* Youth mentors has higher school level than CBT's
* 1/6 Youth mentors had brought manual, compared with 8/14 CBT's
* Only 1 CBT has above 2 (1 st 3) on School, while YM have (2st 0, 1 2st, 2 2st)
* Inverse correlation: CBT old, YM young
* There are no female Youth Mentors (i.e. 100\% male Youth Mentors)
* All of the YM's run their own businesses, compared with 5/10 for CBT's
* Only CBT's said they didn't feel comfortable with smartphone (2 st) - because of age?
* Seemingly no difference CBT vs. YM in when prepares for session
* All YM prepares 2 times for session, while CBT can train also 3 or 1 time)
* 13/14 CBT's gjorde quiz 3 try 1, 6/6 YM's
* YM's och CBT's presterar lika på quiz 3 try 1
* CBT 6/14 st certifierade, YM 4/6 st

Quiz 9 (rött=CBT:
* 6 CBT's gör ej Q9 try 1, 2 YM gör ej
* YM är top performers på Q9 try 1 jämfört med CBT's
* endast 1 YM klarade däremot träningen, medan

* YM's är bättre på quiz 9 try 1 än CBT's
* Det är endast 1/7 som klarade quiz 9 training som är Youth Mentor
* Antal försök man gjorde är likvärdigt, förutom en YM som hade 12 försök (och klarade quiz)
* Det var endast 2 st som klarade certifieringen, och båda dessa var YM och kvinnliga

\textbf{Women}

It is clear from the data that women:
* Have lower education level than the men
* Spread results on the pre-test (probably because of school level)
* Half of them are around 25 years old, half spread out (up until 45 years old)
* 2/6 har eget företag
* Det är bara 1 som ej preppar alls
* 1 st som endast preppar 1 gång, alla andra preppar 2 gånger (3 st) eller 3 gånger (2 st)
* Alla hade max 1 fel på quiz 3 på första försöket!
* De som ej hade rätt, tog det bara 2:a (1 person) eller 3:e försöket (1 person)

* 3/6 gjorde certifieringen - kolla upp: började de?

* Alla förutom 1 tjej gjorde svåraste quizet. De hade minst 42\%! Varav 2 st hade 67\%, 1 hade 50, 1 hade 42, och 1 hade 83

* Quiz 9 tjejerna hade mycket högre lägstanivå () än killarna (, och mycket högre högstanivå än killarna () - tiden är jämförbar, med svag tendens snabbare tjejer
* Av de som hade 50\% på 1:a försöket, gick det betydligt snabbare för tjejerna än killarna att jobba igenom quizet - tyder på att tjejerna är säkrare på materialet än tjejerna - dessutom är det bara 2 killar som fick över 50\% på första försöket
* Om du kollar tvärtom, så är det bara 1 tjej som fick under 50\% på första försöket, medan det var 8 killar
* Quiz 3 syns ej lika tydlig skillnad (OBS: kolla vilken fråga de flesta hade fel på, och kolla om det skiljer sig mellan killar och tjejer)
* Skolnivå verkar oberende på hur quizen blir, om man kollar quiz 9
* Tjejer, antal försök quiz 9 hade de 2 (2 st), 5 (2st, 12 (1st) försök innan de klarade - bland killarna var det 5 (1st) och 7 (1st). Men sedan så var det 0 av killarna som blev certified, men 2 tjejer (de som gjorde på 12 försök och 2 försäk). Att antal försök skiljde sig mellan 2 och 12, men ändå klarar det, berättar att antal försök kanske ej korrelerar. Den på 12 försök hade 70\% på försök, och jobbade igen de 12 försöken väldigt snabbt.
* Den andra tjejen som klarade certifikation quiz 9 klarade 83\% försök 1, (hade tillgång till hjälp), klarade träningen sedan på 2 försök.

Slutsats:
* Anställ bara tjejer. De har högre kunskap och förbereder sig mer, trots lägre skolutbildning.

\textbf{Use of participant and coach manuals}

Användande av appen:
* Vi hittade ingen korrelation quiz-resultat 9 första försöket om man fick hjälp eller inte, antagligen pga att man ej använder manualen före

\textbf{Certified quiz 9}
Only two people were fast enough to get certified on the final quiz before the app evaluation ended.

Characteristics were:
* Both of them used the manual
* Both of them were CBT's, not youth mentors
* Both were women
* They were 24 or 26 years old
* They had a good pre-test score (57\% or 71\%)
* They had top scores (1st place and 2nd place (shared with one other)) on quiz 9 try 1
* They had high scores on quiz 3 try 1 (100\% and 92\%
* They prepared many times per youth session (2 or 3 times)

What didn't seem to matter:
* Number of tries quiz 9 (12 vs 2 on Q9)
* Time to pass training quiz 9 (35.5, slowest vs 12 minutes, below average)
* When day trained (1 trained same day, 1 trained the day before)
* One had a business, one didn't
* School level (1 S?, one S lower)

Other:
* They were medium skilled on using a smartphone
