\chapter{Results}\label{cha:Research}
%

% Ska följa som ett naturligt komplement till huvuddelen

In this chapter the developed application is first demonstrated and explained, and how the app has evolved from iteration 1-4. Then, the results from all the qualitative and quantitative data collection in iteration 1-4 are explained.

 %\todo{Flytta Insights som besvarar en Research Question till Discussion, och hänvisa till iteration. I Resultat vill vi bara ha Resultat, ej svar på forskningsfrågor, så spara svar på forskningsfrågor tills Diskussion.}

%\input{result/example}

\section{The YoungDrive App: Iteration 1-4}\label{developed-application}

  \input{result/application}

In the following sections, you can read more about what data guided the development of the final app, as well as the results from the final app evaluation.

\section{Iteration 1: Uganda Coach Visit}

Here the results from the qualitative and quantitative data for iteration 1 are shown together with conclusions.

\input{result/iteration1/iteration_1_opinions}
\input{result/iteration1/iteration_1_data}
\input{result/iteration1/iteration_1_together}

\section{Iteration 2: Zambia Coach Training}

Here the results from the qualitative and quantitative data for iteration 2 are shown together with conclusions.

\input{result/iteration2/iteration_2_opinions}
\input{result/iteration2/iteration_2_data}
\input{result/iteration2/iteration_2_bloom}
\input{result/iteration2/iteration_2_together}

\section{Iteration 3: Uganda Formative Test}

Here the results from the qualitative and quantitative data for iteration 3 are shown together with conclusions. For the coach training in iteration 1, designing the app only for assessment but not for improvement was acceptable, since Josefina could give feedback in person. This meant that scoring low (like 5/10) or high (like 9/10) on a quiz after a session, the coach not taking the quiz again was not mandatory. Josefina could observe the results, and complement the missing information in an upcoming lecture or give immediate feedback herself.

In contrast, image the situation of using the app being weeks or months \textit{after} the training, and Josefina is no longer available. Instead, the coach uses the app exclusively one hour before a youth session, to assess if the coach is ready. If a coach receives the score 5/10 or 9/10, what should happen? Clearly, in this case the app should be designed to not leave the coach alone, but help the coach to get smart feedback, encourage the coach to try again and improve their score, and again assess if the coach is fully ready for teaching the youth in the given topic. This new design of the app was the focus of the interactions from iteration 3, the results observable below.

\input{result/iteration3/iteration_3_opinions}
\input{result/iteration3/iteration_3_data}
\input{result/iteration3/iteration_3_workshops}
\input{result/iteration3/iteration_3_together}

\section{Iteration 4: Uganda Summative Test}

Here the results from the qualitative and quantitative data for iteration 4 are shown together with conclusions. In these activities, there were 25 coaches present during both the app test and the interviews.

\input{result/iteration4/iteration_4_data}

\input{result/iteration4/iteration_4_opinions}
%\input{result/iteration4/iteration_4_together}

%For Discussion, Conclusion and Future Work, see the coming chapters.

%\section{Qualitative Data}
%
%  Here the results from the qualitative data for iteration 1, 2, %3 and 4 are shown.
%
%  \input{result/iteration_1_opinions}
%  \input{result/iteration_2_opinions}
%  \input{result/iteration_3_opinions}
%  \input{result/iteration_4_opinions}
%
%\section{Quantitative Data}
%
%  Here the results from the quantitative data for iteration 1, 2, %3 and 4 are shown.
%
%  \input{result/iteration_1_data}
%  \input{result/iteration_2_data}
%  \input{result/iteration_3_data}
%  \input{result/iteration_4_data}
%
%\section{Insights}
%
%  \input{result/iteration_1_together}
%  \input{result/iteration_2_together}
%  \input{result/iteration_3_together}
%  \input{result/iteration_4_together}

%\begin{chapter-appendix}

%\input{appendix/proof_appendix}

%\end{chapter-appendix}
