\begin{acknowledgments}
%Fakta om rapportens tillkomst.
%Tacka personer som hjälpt till med informations- eller språkgranskning.
%Säg inget om resultat, slutsatser, syfte eller andra uppgifter

  Due to a chain of lucky events, this master thesis took the approach of combining service design, thoughtful interaction design, technology, learning effectiveness research, and entrepreneurship.

For service design, I want to thank Peter Gahnström at LiU Innovation leading me to Expedition Mondial. There I especially want to thank Susanna Nissar for being a great tutor, and also Erik Widmark.

Thoughtful interaction design was introduced thanks to a recommendation from Lena Tibell and Konrad Schönborn, to go to Jonas Löwgren's first test lecture about interaction design at Linköping University, which led me to looking deeper into his literature, and discovering the book Thoughtful Interaction Design, which was a perfect fit into the world of interaction design for me, coming from an engineering perspective. It showed me what being a great designer really meant, and I was compelled.

For learning effectiveness research, I greatly want to thank Lena Tibell and Konrad Schönborn. Henrik Marklund at Knowly has also provided a valuable perspective on digital learning.

For entrepreneurship education, I have so many to thank, including again Konrad Schönborn. But by biggest thanks goes to those that knew the entrepreneurship coaches: Josefina Lönn and Iliana Björling from YoungDrive, and Gerald Emoyo from Plan International. Also, Julien Tantege from Grameen Foundation in Kampala shared her experience working with technology targeting the very same coaches.

Thank you for your contributions! Lastly but not least, I want to thank Linnea Rothin who put me right track on the master thesis, and to Lena Tibell and Konrad Schönborn who has been supervising this master thesis from start to end. Your expertise and continuous feedback has been incredibly valuable, and I feel honoured to have been given this learning opportunity.

Thank you.

% Se t.ex. exjobbet "Development of handheld mobile applications for the public sector" av Fredrik Bergström och Gustav Engvall

  \addvspace{1em}
  \begin{flushright}
    \textit{%
      Norrköping, August 2016\\
      Marcus Nygren%
    }
  \end{flushright}
\end{acknowledgments}
