\subsection{Methods to Design for Motivation}

Social psychology can guide the design when there is a wish to make people behave differently. One of the biggest areas of research is motivation psychology.

Motivation is commonly divided into three areas:
\begin{itemize}
\item Self-determination - the students inner motivation, genuine wishes
\item Achievement - the students motivation to achieve
\item Expectation value - the expectations on the student
\end{itemize}

Koballa \citep{koballa} and Abell \citep{abell} gives an overview of theories developed for these three fields. Further, Fulmer \citep{fulmer} provides a review of methods to collect data which can be used to study motivation.

Deci \citep{deci} and Ryan \citep{ryan} studies self-determination theory, Elliot \citep{elliot} studies achievement theory, and Eccles \citep{eccles} and Wigfield \citep{wigfield} studies expectancy-value theory.

If you have designed for the user's compelling context, Sierra says, the users are already motivated. Their motivation is to become better (achieve). \citep{sierra}.

In terms of effective learning and expectation value, a growing research field is training transfer \citep{brinkerhoff}. Before and after is as important as the training itself. To design for this, the leader should be involved with the participants before the training, and communicate expectations. The student should be expected to implement the training in everyday life. \citep{brinkerhoff}

Sierra \citep{sierra}, suggests the focus to be how to help users progress (see "Progress and payoffs", achieve), and what pulls them off (see "Cognitive load theory").

\subsubsection{Cognitive load theory}

Sierra argues working on what stops people, matters more than working on what entices them. Thus, a focus needs to be identifying and removing blocks.

Sierra \citep{sierra} describes how humans have scarce cognitive resources, and how to design for these.

Cognitive load theory (CLT) research is divided into three areas: intrinsic CLT (stumbling blocks), extrinsic CLT, and germane CLT. Below, to design for these are described.

Intrinsic CLT, needs to be dealt with if the effort is too high. Sierra \citep{sierra}describes two strategies. She first says that according to deliberate practice, if you can not get to 95\% reliability within three 45-90 minute sessions, split skills that can be done with effort into sub-skills. The purpose is to reduce time spent practising being mediocre.

Extraneous CLT, is about the way information is presented to a learner, and should be handled via designing to support cognitive resources, Sierra says \citep{sierra}.

Germane CLT, is the work put into creating a permanent store of knowledge. To support cognitive resources, escape the brain's spam filter by making the information essential. Either by designing for the compelling context, or desining for just-in-time learning versus just-in-case, Sierra says. \citep{sierra}

Scaffolding is a technique to step by step remove the support wheels for the user, e.g. present information in different ways. Clark's \citep{gates} report shows that in their research, each category of scaffolding demonstrated significant effects on learning.

Another way to reduce cognitive leaks is don't make users memorise unnecessary things: make the thing you want the user to do, the most likely thing to do (affordances). Everything that takes willpower, reduces cognitive leaks.

In the case of an quiz app, the visual presentation of the questions can reduce extraneous load by removing unnecessary information. Germane load can be increased by giving scaffolding support at the end of each section, for example helping users to remember, by showing them their answers.

The rule of thumb is that you want to decrease extraneous load (bad load), and increase germane load (good load).

\subsubsection{Progress and payoffs}

Sierra argues that to pull users forward, to stay motivated, progress and payoffs are essential. Both of these, are investigated in terms of motivational psychology.

The feeling of progress can be emphasised by a path with guidelines to help the user know where they are at each step, e.g. for a training. To create a path, she encourages the designer to make a list of key skills ordered from beginner to expert. Then, these are sliced into groups of ranking or levels.

This way, it is possible to design a “belt” path for your context. The first level, should feel like a superpower for the user. The best payoff, is a intrinsically rewarding experiences, according to Sierra \citep{sierra}. For an entrepreneur, gaining the skills of selling (the progress) can be as rewarding as having gained the money for it (the payoff).

For motivation, the earlier, lower levels should be achievable in far less time and effort than the later, advanced levels. One practice is to try to have each new level take roughly double the time and effort of the previous level. This highly relates to flow.

Caring for the compelling context, why the user wants to learn the skill, are helpful strategies. A sometimes critiqued way of progression is to give the user high pay-off tips, but if done in a fair way, it is a good way for both learning and motivation.

This kind of path map is suberb to simple gamification, says Sierra \citep{sierra}. In an app for building entrepreneurship coach skills, the act of becoming certified (getting 100\% correct), might not be as rewarding as the progress of getting there. Therefore, gamification of the sort "rewarding effort" might be more beneficial with "rewarding result". Suitable gamification could also mean unlocking new possibilities of adding value to the app (for example adding questions to the quiz), versus getting a badge or a star.

The shown benefits of designing for intrinsic motivation is in-line with self-determination theory \citep{deci} \citep{ryan}.  Pink \citep{pink} says that the surprising truth about what motivates us is that drive is fostered by autonomy, mastery and purpose. Meanwhile, Clark \citep{gates} says that simple gamification as well as more sophisticated game mechanics can prove effective. However, he adds that it should be investigated if "simple gamification" (e.g. contingent point and badges connected to learning activities) more frequently focus on lower-order learning outcomes, compared to studies with more sophisticated game mechanics. For the case of entrepreneurship, the goal is on higher-order learning outcomes, meaning simple gamification is not enough to motivate users. Thus, if you do not design for the compelling context, entrepreneurship coaches may well prefer other learning methods instead of using your gamified app.
